How Attention Impact Language Learning Tasks? \\ A Visual Analytics Tool for Interpreting, Debugging, \\ and Tunning Text Entailment Model

### 2018-01-19 paper/paper_entailVis.tex
add layout

%% Abstract section.
\abstract{

@@

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{Natural Language Processing}

@@

%% if specified like this the section will be committed in review mode
\acknowledgments{
The authors wish to thank A, B, and C. This work was supported in part by
a grant from XYZ (\# 12345-67890).}

>>>>

%% Abstract section.
\abstract{
In Natural Language Processs (NLP) research attention mechanism has gained a
strong following,

@@

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{Natural Language Processing, Interpretable Machine Learning,
Visual Analytics}

@@

%% if specified like this the section will be committed in review mode
% \acknowledgments{
% The authors wish to thank A, B, and C. This work was supported in part by
% a grant from XYZ (\# 12345-67890).}
